The Occurrence of Earth-Like Planets Around Other Stars

### 2014-04-18 paper/kepler-selection.tex
Use automatically-produced X +/- Y quantities.

@@

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period at one
  Earth radius and one year periods, describes the occurrence of
  Earth-like extrasolar planets.  Measurement of $\etaearth$ is
  complicated by the difficulty of detecting Earth-like planets in
  Earth-like orbits about Sun-like stars.  Previous
  estimates\cite{2011ApJ...738..151C,2012ApJ...745...20T,2013ApJ...778...53D,2013PNAS..11019273P}
  place $1\% \lesssim \etaearth \lesssim 34\%$.  These works dealt
  with the problem of selection effects in the sample by either
  analyzing a region of the period-radius parameter space where
  observations are complete and extrapolating to $R = \REarth$ and $P
  = 1 \mathrm{yr}$\cite{2011ApJ...738..151C,2012ApJ...745...20T} or
  applying a binned analysis in the period-radius
  plane\cite{2013ApJ...778...53D,2013PNAS..11019273P}.  Here we
  present constraints on $\etaearth$ from a parameterised forward
  model of the (correlated) period-radius distribution and the
  observational selection function in the most recent (Q17) data
  release from the Kepler
  satellite\cite{2010Sci...327..977B,2011ApJ...736...19B,2013ApJS..204...24B}.
  Our data set comprises 181,568 systems observed under the Kepler
  exoplanet observing program, producing 2598 planetary candidates.
  We parameterise the distribution of planetary periods and radii
  using a single, correlated Gaussian component; treat selection
  effects using a parameterised transit detection probability based on
  the measured noise level and stellar properties in the Kepler
  catalog; and include an empirically-parameterised, independent
  component in the planet period-radius distribution to represent
  false-positive planet detections.  Using our model we can
  simultaneously estimate $\etaearth$, place constraints on the planet
  period-radius distribution function, and determine the degree of
  contamination by false-positive candidate indentifications.  We find
  $\etaearth = 3.8^{+2.1}_{-1.6}\%$ (90\% CL).  Additionally, we find
  that each star hosts $3.82_{-0.60}^{+0.70}$ planets with $P \lesssim
  3 \mathrm{yr}$ and $R \gtrsim 0.2 \REarth$, that the peak of the
  planet radius distribution lies at $\Rpeak = 1.25_{-0.17}^{+0.16}
  \REarth$, and that $\ln P$ and $\ln R$ are correlated with
  correlation coefficient $r = 0.335_{-0.054}^{+0.052}$ (all 90\% CL).
  Our empirical model for false-positive contamination is consistent
  with the dominant source being backgroud eclipsing binary
  stars\cite{2013ApJ...766...81F}, with $7.8_{-1.3}^{+1.4}\%$ (90\%
  CL) of the candidates being false-positives.
\end{abstract}

\begin{figure}
  \includegraphics[width=\columnwidth]{eta-earth}
  \caption{\label{fig:eta-earth} \textbf{The posterior on $\etaearth$
      accounting for selection effects and false positives.}  Recall
    that $\etaearth \equiv \left. \frac{dN_\mathrm{pl}}{d\ln P \,d \ln
      R} \right|_{P = 1\mathrm{yr}, R=1\REarth}$.  Vertical lines
    indicate the 90\% credible range.  We find $\etaearth =
    3.8^{+2.1}_{-1.6}\%$, slightly lower than but consistent with
    previous work\cite{2013PNAS..11019273P}.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{npl}
  \caption{\label{fig:npl} \textbf{The posterior on $\Rpl$.}  Recall
    that $\Rpl$ is the number of planets per star.  Vertical lines
    indicate the 90\% credible range.  We find $\Rpl =
    3.82_{-0.60}^{+0.70}$. \Will{CITE/discuss previous work.}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{foreground-dist}
  \caption{\label{fig:foreground-dist} \textbf{The inferred planet
      period-radius distribution accounting for selection effects and
      false-positives.}  (Upper Left) The planet number density per
    logarithmic planet radius.  The density peaks at $\Rpeak =
    1.19_{-0.18}^{+0.17} \REarth$ (90\% CL).  (Upper Right) The planet
    number density in the period-radius plane.  The inferred
    correlation coefficient between $\ln P$ and $\ln R$ is $r =
    0.335_{-0.054}^{+0.052}$.  (Lower Left) Scatter plot of the radius
    and period of the Kepler planet candidates.  Color indicates the
    posterior false-positive probability for each candidate.  Overall,
    the model prefers a false-positive rate of $7.8_{-1.3}^{+1.4}\%$
    (90\% CL).  The primary contaminant is probably background
    eclipsing binaries; our rate is consistent with previous
    work\cite{2013ApJ...766...81F}. (Lower Right) The planet number
    density per logarithmic planet period.  The density peaks at $P =
    0.075_{-0.006}^{+0.007}\mathrm{yr}$.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{selection}
  \caption{\label{fig:selection} \textbf{Comparison of synthetic data
      sets produced from the forward model incorporating selection
      effects with observed candidates.}  (Upper Left) The observed
    (black curve) and synthetic (blue curve; including planets and
    false positives, and using the fitted selection model to
    down-select the candidates from the planet distribution)
    normalised candidate density per logarithmic radius.  Except for a
    discrepancy at $R \simeq 10 \REarth$---associated with hot
    Jupiters, a distinct planetary population\Will{CITE, and
      check}---the model produces a good fit to the observed
    candidates over the range of reported radii.  (Upper Right)
    Scatter plot of the observed candidates (black circles) and a
    posterior-averaged draw of candidates from the model (blue
    circles).  (Lower Left) Scatter plot of the observed candidates.
    Colors indicate the posterior-averaged selection probability for
    each planet about its host star.  Recall that the selection
    probability is treated a product of a geometric factor giving the
    probability of an isotropically-oriented orbit producing a transit
    and a signal-to-noise-ratio-dependent transit detection
    probability.  (Lower Right) The observed (black curve) and
    synthetic (blue curve; including planets and false positives, and
    using the fitted selection model to down-select the candidates
    from the planet distribution) normalised candidate density per
    logarithmic period.  Except for the aforementioned hot Jupiter
    peak at $P \simeq 1 \mathrm{day}$ the model produces a good fit to
    the observed candidates over the range of reported periods.}
\end{figure}

>>>>

\input{quantities}

@@

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period at one
  Earth radius and one year periods, describes the occurrence of
  Earth-like extrasolar planets.  Measurement of $\etaearth$ is
  complicated by the difficulty of detecting Earth-like planets in
  Earth-like orbits about Sun-like stars.  Previous
  estimates\cite{2011ApJ...738..151C,2012ApJ...745...20T,2013ApJ...778...53D,2013PNAS..11019273P}
  place $1\% \lesssim \etaearth \lesssim 34\%$.  These works dealt
  with the problem of selection effects in the sample by either
  analyzing a region of the period-radius parameter space where
  observations are complete and extrapolating to $R = \REarth$ and $P
  = 1 \mathrm{yr}$\cite{2011ApJ...738..151C,2012ApJ...745...20T} or
  applying a binned analysis incorporating survey incompletness in the
  period-radius plane\cite{2013ApJ...778...53D,2013PNAS..11019273P}.
  Here we present constraints on $\etaearth$ from a parameterised
  forward model of the (correlated) period-radius distribution and the
  observational selection function in the most recent (Q17) data
  release from the Kepler
  satellite\cite{2010Sci...327..977B,2011ApJ...736...19B,2013ApJS..204...24B}.
  Our data set comprises 181,568 systems observed under the Kepler
  exoplanet observing program, producing 2598 planetary candidates.
  We parameterise the distribution of planetary periods and radii
  using a single, correlated Gaussian component; treat selection
  effects using a parameterised transit detection probability based on
  the measured noise level and stellar properties in the Kepler
  catalog; and include an empirically-parameterised, independent
  component in the planet period-radius distribution to represent
  false-positive planet detections.  Using our model we can
  simultaneously estimate $\etaearth$, place constraints on the planet
  period-radius distribution function, and determine the degree of
  contamination by false-positive candidate indentifications.  We find
  $\etaearth = \earange$ (90\% CL), in agreement with
  Ref.\ \cite{2013PNAS..11019273P}.  However, in contrast to
  Ref.\ \cite{2013PNAS..11019273P}, we can conclude that each star
  hosts $\rplrange$ planets with $P \lesssim 3 \mathrm{yr}$
  and $R \gtrsim 0.2 \REarth$, that the peak of the planet radius
  distribution lies at $\Rpeak = \rpeakrange \REarth$, and
  that $\ln P$ and $\ln R$ are correlated with correlation coefficient
  $r = \corrcoeffrange$ (all 90\% CL).  Our empirical model
  for false-positive contamination is consistent with the dominant
  source being backgroud eclipsing binary
  stars\cite{2013ApJ...766...81F}, with $\fposrange$ (90\%
  CL) of the candidates being false-positives.
\end{abstract}

\begin{figure}
  \includegraphics[width=\columnwidth]{eta-earth}
  \caption{\label{fig:eta-earth} \textbf{The posterior on $\etaearth$
      accounting for selection effects and false positives.}  Recall
    that $\etaearth \equiv \left. \frac{dN_\mathrm{pl}}{d\ln P \,d \ln
      R} \right|_{P = 1\mathrm{yr}, R=1\REarth}$.  Vertical lines
    indicate the 90\% credible range.  We find $\etaearth = \earange$,
    in agreement with previous work\cite{2013PNAS..11019273P}.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{npl}
  \caption{\label{fig:npl} \textbf{The posterior on $\Rpl$.}  Recall
    that $\Rpl$ is the number of planets per star.  Vertical lines
    indicate the 90\% credible range.  We find $\Rpl =
    \rplrange$. \Will{CITE/discuss previous work.}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{foreground-dist}
  \caption{\label{fig:foreground-dist} \textbf{The inferred planet
      period-radius distribution accounting for selection effects and
      false-positives.}  (Upper Left) The planet number density per
    logarithmic planet radius.  The density peaks at $\Rpeak =
    \rpeakrange \REarth$ (90\% CL).  (Upper Right) The planet
    number density in the period-radius plane.  The inferred
    correlation coefficient between $\ln P$ and $\ln R$ is $r =
    \corrcoeffrange$.  (Lower Left) Scatter plot of the radius
    and period of the Kepler planet candidates.  Color indicates the
    posterior false-positive probability for each candidate.  Overall,
    the model prefers a false-positive rate of $\fposrange$
    (90\% CL).  The primary contaminant is probably background
    eclipsing binaries; our contamination rate is consistent with
    previous work\cite{2013ApJ...766...81F}. (Lower Right) The planet
    number density per logarithmic planet period.  The density peaks
    at $P = \ppeakrange \mathrm{yr}$ (90\% CL).}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{selection}
  \caption{\label{fig:selection} \textbf{Comparison of synthetic data
      sets produced from the forward model incorporating selection
      effects with observed candidates.}  (Upper Left) The observed
    (black curve) and synthetic (blue curve; including planets and
    false positives, and using the fitted selection model to
    down-select the candidates from the planet distribution)
    normalised candidate density per logarithmic radius.  Except for a
    discrepancy at $R \simeq 10 \REarth$---associated with hot
    Jupiters, a distinct planetary population\Will{CITE, and
      check}---the model produces a good fit to the observed
    candidates over the range of reported radii.  (Upper Right)
    Scatter plot of the observed candidates (black circles) and a
    posterior-averaged draw of observed candidates from the model
    (blue circles).  (Lower Left) Scatter plot of the observed
    candidates.  Colors indicate the posterior-averaged selection
    probability for each planet about its host star.  Recall that the
    selection probability is treated a product of a geometric factor
    giving the probability of an isotropically-oriented orbit
    producing a transit and a signal-to-noise-ratio-dependent transit
    detection probability.  (Lower Right) The observed (black curve)
    and synthetic (blue curve; including planets and false positives,
    and using the fitted selection model to down-select the candidates
    from the planet distribution) normalised candidate density per
    logarithmic period.  Except for the aforementioned hot Jupiter
    peak at $P \simeq 1 \mathrm{day}$ the model produces a good fit to
    the observed candidates over the range of reported periods.}
\end{figure}
